### 2021-12-20 input/experiments.tex
about algo
update figure, not nearly done though

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe. The generated trace marked with red dots starts from
    Lisboa to reach Copenhagen 10 seconds later.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}\TODO{PLACEHOLDER}
    \TODO{Experiment with ascast against xascast?}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.}}
\end{figure*}

>>>>

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}. The generated trace marked with
    red dots starts from Lisboa to reach Copenhagen 10 seconds
    later.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}\TODO{PLACEHOLDER}
    \TODO{Experiment with ascast against xascast? with different cache
      size}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/xas_cast_line.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
\end{figure*}
